animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2025-07-11 response_to_review.qmd

- *Page 2, paragraph starting with Hvitfeldt: it might be helpful to include parts of the example from Hvitfeldt, or at least describe what parts of the example inspired animbook*

Response: We have emphasized that his example code that reproduces the New York Times visualization inspires this package.

- *Page 2, paragraph starting with "In the data structure": I suggest a little more pretext for the example of company name and where the company is registered. Or state the purpose of ID and grouping before giving a cohesive example.*

Response: Text has been modified to include an example using the US and Japan osiris data.

@@

- *Page 18: There is a reference starting with "---------" that should be filled in.*

Response: Fixed

- *An example with the funnel_web_plot() would be a nice addition in the applications section.*

Response: We would rather not because it is experimental and retained in the package in case it is useful at some point.

@@

- *When using custom breaks, the error displays "The breaks vector must have the same number of groups as ncat argument", but it is stated in the article that the length of breaks need to equal the number of categories plus 1.*

Response: The code has been fixed.

- *When running the code on an M1 MacBook Pro, some of the shaded sections tear apart and look like white circles. This happens particularly with the wallaby plots.*

Response: We are not sure what is happening here. We have tested on an M1 MacBook Pro and don't see the problem. Ideally this sort of problem is reported as an issue on the package website with a small code example.

### 2025-07-11 animbook-journal.Rmd
macbook issue response

Two real-world examples of usage are provided. The osiris example studies company movement between quartiles of sales performance over a 12-year period. The voting example studies party preference changes between the 2016 and 2019 elections.

@@

The Osiris data presented in this section was acquired from Bureau van Dijk (@bvd), compiling information on a total of 122,318 companies. It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables. The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018. The variables in this dataset include year, ID, country, sales, and the binary variable called japan.

>>>>

Two real-world examples of usage are provided. The Osiris [@bvd] example studies company movement between quartiles of sales performance over a 12-year period. The voting example studies party preference changes between the 2016 and 2019 elections.

@@

The full Osiris provides information on a total of 122,318 companies.  The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018. The variables in this dataset include year, ID, country, sales, and the binary variable called japan.
